A weakly structured stem for human origins in Africa

### 2022-03-07 paper.tex
Update paper.tex
Modified the last paragraph and added citations in comments.

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb} (see also Section \ref{morpho_diff}). The fossil
record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to present-day humans (e.g., from Omo
Kibish, Ethiopia), others are similar in some features but not others (e.g.,
from Jebel Irhoud, Morocco), and others are very different (e.g., from
Dinaledi, South Africa) in morphology. If, as our model predicts, the
morphological differences between the stems were comparable to those among
present-day human populations, the most divergent fossils are unlikely to
represent branches that contributed appreciably to present-day human
ancestries.

>>>>

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb} (see also Section \ref{morpho_diff}). This correspondence allows predictions of our model to be related to the fossil record. The fossil
record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to present-day humans (e.g., from Omo
Kibish, Ethiopia\tdwcomment{add citations: Day (1969) doi.org/10.1038/2221135a0 and Vidal et al. (2022) doi.org/10.1038/s41586-021-04275-8}), others are similar in some features but not others (e.g.,
from Jebel Irhoud, Morocco\tdwcomment{add citations: Hublin et al. (2017) doi.org/10.1038/nature22336 and Richter et al. (2017) doi.org/10.1038/nature22335}), and others are very different (e.g., from
Dinaledi, South Africa\tdwcomment{add citations: Berger et al. (2015) doi.org/10.7554/eLife.09560 and Dirks et al. (2017) doi.org/10.7554/eLife.24231.001}) in morphology. If, as our model predicts, the
genetic differences between the stems were comparable to those among
present-day human populations, the most morphologically divergent fossils are unlikely to
represent branches that contributed appreciably to present-day human
ancestries.
